\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-07 doc/sw-system.tex
Added note on stars, closes #171
Fixed #173

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{minipage}{0.48\linewidth}
  \centering\includegraphics[width=\linewidth]{stage1_ROC.pdf}
\end{minipage}\hfill
\begin{minipage}{0.48\linewidth}
  \centering\includegraphics[width=\linewidth]{stage2_ROC.pdf}
\end{minipage}
\caption{Receiver operating characteristic curves for the \SW system, using
the \cfhtls training set. Left: \StageOne, right: \StageTwo. Insets show a
magnified view of the top lefthand corner of each plot. Linestyles illustrate
the agent properties (initial confusion matrix elements, learning or not)
discussed in the text, as well as the difference between the online and offline
analyses. The \StageTwo sample was defined using the online \StageOne results
(solid blue curve), while the offline analysis was chosen for the final
\StageTwo results (dot-dashed orange curve). }
\label{fig:results:sample:roc}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Finally, there could be some performance gains to be made by improving the SWAP
agent model, or its implementation. Low skill is typically a result  of
inexperience (\Sref{sec:results:crowd}), but it could be the agent that is
inexperienced as well as the classifier or its agent. In a future paper we plan
to investigate the use of the test images as well as the training images in
accelerating the agent's learning (Davis et al, in preparation). We also plan to
investigate the use of offline analysis at \StageOne, partly for the same reason
(see also \Sref{sec:discuss:efficiency} below.) Given the above findings  about
the effects of noise in the SWAP system, we are also motivated to explore
further the possible noise-reducing effects of the doing the analysis offline
(\Sref{sec:results:sample}).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{minipage}{0.48\linewidth}
  \centering\includegraphics[width=\linewidth]{stage1_ROC.pdf}
\end{minipage}\hfill
\begin{minipage}{0.48\linewidth}
  \centering\includegraphics[width=\linewidth]{stage2_ROC.pdf}
\end{minipage}
\caption{Receiver operating characteristic curves for the \SW system, using
the \cfhtls training set. Left: \StageOne, right: \StageTwo. Insets show a
magnified view of the top lefthand corner of each plot. Linestyles illustrate
the agent properties (initial confusion matrix elements, learning or not)
discussed in the text, as well as the difference between the online and offline
analyses. The \StageTwo sample was defined using the online \StageOne results
(solid blue curve), while the offline analysis was chosen for the final
\StageTwo results (dot-dashed orange curve).
Lens probability varies along the curves: the stars indicate the point where
the value of this quantity is 0.95.}
\label{fig:results:sample:roc}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Finally, there could be some performance gains to be made by improving the SWAP
agent model, or its implementation.

Low skill is typically a result  of inexperience (\Sref{sec:results:crowd}) --
but it could be the agent  that is inexperienced, as much  the classifier.  In a
future paper we plan to investigate the use of the test images as well as the
training images in accelerating the agent's learning (Davis et al, in
preparation). We also plan to investigate the use of offline analysis at
\StageOne, partly for the same reason (see also \Sref{sec:discuss:efficiency}
below.) Given the above findings  about the effects of noise in the SWAP system,
we are also motivated to explore further the possible noise-reducing effects of
the doing the analysis offline (\Sref{sec:results:sample}).
